---
title: "Check Globus Renaming Log File"
format: html
author: "Heidi Rodenhizer"
---

# Set Up

```{r}
library(tidyverse)
```

# Load Data
```{r}
rename_log = read_delim(
  "./data/globus_rename_log.txt",
  delim = " -> ",
  col_names = c("status_from", "to_exit_code")
) |>
  separate_wider_delim(
    status_from,
    delim = " ",
    names = c("status", "from"),
    too_many = "merge"
  ) |>
  separate_wider_delim(
    to_exit_code,
    delim = " ",
    names = c("to", "exit_code"),
    too_few = "align_start",
    too_many = "merge"
  ) |>
  mutate(
    across(
      everything(),
      ~ str_trim(.x, side = "both")
    ),
    manifest = str_detect(from, "manifest")
  ) |>
  arrange(from)

renaming_manifest = read_csv(
  "./data/planet_globus_renaming_manifest.csv",
  col_names = c("from", "to")
)

manifest_renaming_manifest = read_csv(
  "./data/planet_globus_manifest_renaming_manifest.csv",
  col_names = c("new_from", "to")
)

file_cache = read_delim(
  "./data/existing_files_cache.txt",
  " ",
  col_names = c("file")
)
batch_file = read_delim("./data/batch_transfer.txt", " ")
```

```{r}
log_succeeded = rename_log |>
  filter(status == "[SUCCESS]")

log_failed = rename_log |>
  filter(status == "[FAILED]")

log_skipped = rename_log |>
  filter(status == "[SKIPPED]")
```

# Check if All Files Eventually Succeeded
```{r}
renaming_manifest = renaming_manifest |>
  left_join(manifest_renaming_manifest, by = c("to")) |>
  mutate(
    from = case_when(
      !is.na(new_from) ~ new_from,
      TRUE ~ from
    )
  )

did_not_succeed = renaming_manifest |>
  anti_join(log_succeeded, by = c("from", "to")) |> 
  select(-new_from)

# write_csv(
#   did_not_succeed,
#   "./data/globus_rename_lost_files.csv"
# )

# Manual inspection of a handful of cases showed a failure marked down, followed by a skipped file, and the file does show up in the new location
succeed_not_recorded = did_not_succeed |>
  right_join(log_skipped, by = c("from", "to"))
# remove the cases where it said it failed and then was skipped, because they probably aren't real
actual_failures = did_not_succeed |>
  anti_join(succeed_not_recorded, by = c("from", "to"))
```

```{r}
fail_not_recorded = did_not_succeed |>
  anti_join(log_failed, by = c("from", "to"))

fail_recorded = did_not_succeed |>
  right_join(log_failed, by = c("from", "to"))

nrow(fail_not_recorded) + nrow(fail_recorded) == nrow(did_not_succeed)
```

# Problems with Manifests
The first manifest renaming worked, but following copies didn't work because the "from" file had been removed already.
Create a new manifest to rename the manifests by copying the new location of the first copy into the "from" column for all the failed renames.

```{r}
manifests = rename_log |>
  filter(manifest == TRUE) |>
  mutate(
    from = case_when(
      status == "[FAILED]" ~ first(to),
      TRUE ~ NA
    ),
    .by = from
  ) |>
  filter(!is.na(from)) |>
  mutate(
    year = str_extract(
      from,
      "(?<=/global_quarterly/)\\d{4}(?=/q3/)"
    )
  )

manifests_by_year = manifests |>
  summarise(
    count = n(),
    .by = year
  ) |>
  mutate(
    percent = count / sum(count)
  )

nrow(actual_failures) == nrow(manifests)

manifests_succeeded = log_succeeded |>
  filter(manifest == TRUE) |>
  mutate(
    duplicate = row_number(),
    .by = c(from)
  ) |>
  arrange(from, duplicate)

# write_csv(
#   manifests |>
#     select(from, to),
#   "./data/planet_globus_manifest_renaming_manifest.csv",
#   col_names = FALSE
# )
```

# The Other Failed Files

```{r}
data_files_to_redo = did_not_succeed |>
  filter(manifest == FALSE)

# write_csv(
#   data_files_to_redo |>
#     select(from, to),
#   "./data/planet_globus_renaming_manifest_failed_file_redo.csv",
#   col_names = FALSE
# )
```

# Find Directories to Delete

```{r}
directories_to_delete = renaming_manifest |>
  select(from) |>
  rowwise() |>
  mutate(
    from_dir = str_flatten(
      str_split(
        from,
        "/",
        simplify = TRUE
      )[1:4],
      collapse = "/"
    )
  ) |>
  ungroup() |>
  distinct() |>
  select(from_dir)

# write_csv(
#   directories_to_delete,
#   "./data/directories_to_delete_globus.csv",
#   col_names = FALSE
# )
```